Energy aware HPC

### 2021-03-25 thesis/fingerprint/fingerprint.tex
rename figures

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fingerprint/figures/PERF_COUNT_HW_INSTRUCTIONS.png}
    \caption{Multiple executions of the Polybench 2mm program with different input sizes}
    \label{fig:multiple_exec}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fingerprint/figures/PERF_COUNT_HW_INSTRUCTIONS_1.png}
    \caption{Single instance representation}
    \label{fig:single_curve}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fingerprint/figures/PERF_COUNT_HW_INSTRUCTIONS_2.png}
    \caption{Interpolation}
    \label{fig:interporlation}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fingerprint/figures/PERF_COUNT_HW_INSTRUCTIONS_3.png}
    \caption{Filtering}
    \label{fig:filtering}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fingerprint/figures/workflow.png}
    \caption{Multiple executions of the Polybench 2mm program with different input sizes}
    \label{fig:multiple_exec}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fingerprint/figures/workflow_1.png}
    \caption{Single instance representation}
    \label{fig:single_curve}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fingerprint/figures/workflow_2.png}
    \caption{Interpolation}
    \label{fig:interporlation}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fingerprint/figures/workflow_3.png}
    \caption{Filtering}
    \label{fig:filtering}
\end{figure}
